
\chapter{Acknowledgments}

The work I present here could not have been possible without the support of my supervisors Prof. Jan Carmeliet, Dr. Dominique Derome, Dr. Jonas Allegrini, and Prof. Dr. Thijs Defraeye. I would like to thank Jan for giving me the opportunity to pursue a challenging research that called for multiple skill sets. His supervising formed a part of my PhD life, helping me become a researcher and person that I am now. I would like to also thank Dr. Dominique Derome for her role in my PhD. 

I would like to especially thank my daily, and sometimes even hourly supervision by Thijs :). Your guidance was an integral part during my PhD. You have provided me advice, guidance, perspective, and confidence during an key part of my life. At times of my shortcomings, you have encouraged me to reflect and address those issues. And times of lack of confidence, you have given me confidence to build my strengths. I would like to say you have been a great mentor in my life and hope others maybe equally lucky in future. 

I would like to thank the company of researches who I had to fortune to meet: Dr. Andrea Radu, Dr. Aytac Kubilay, Dr. Karol Kulasinski, Dr. Jaebong Lee, Dr. Marc Immer, Dr. Marcel Vonlanthen, Dr. Sreeyuth Lal, Dr. Soyoun Son, Dr. Boran Morvaj, Dr. Georgios Mavromatidis, Dr. Marc Hohmann, Dr. Omid Dorostkar, Dr. Somil Miglani, Dr. Christoph Waibel, Dr. Julien Marquant, Dr. Marcelo Parada, Dr. Laure Lemrich, Dr. Kevin Prawiranto, Christian Kanesan, Giovanni Langella, Chi Zhang, Mingyang Chen, Gianluca Mussetti, Dominik Strebel, Ali Shomali, Portia Murray, Cristina Dominguez Hernandez, Robert Fischer, Dr. Yongling Zhao, Dr. Andrea Ferrari, Dr. Jianlin Zhao, Dr. Xiaohai Zhou, Monika Dash, Dr. Adriana Chitez, Dr. Wentao Wu, Jiggar Shah, Pasha Piroozmand, Christina Tsalicoglou, Ishaan Markale, Amir Ashrafi, Dr. Ali Mazloomi, Mehrshad Foroughan, Giorgia Tagliavini, Giorgia Tagliavini, Hamed Almohammadi, Jigar Parekh, Nilesh Sawant, Michael Fehr, Guylaine Desmarais, Danhong Wang, Felix B\"unning, and Viktor Dorer. 

My gratitude also goes out to Stephan Carl for offering his assistance whenever it was needed the most. I've enjoyed the fun and perhaps the important time we spend together in the lab planning and testing curious little setups important for my PhD. I would like to acknowledge the technical assistance of Roger Vonbank and Beat Margelisch. I owe special thanks to Martina Koch for her prompt and cheerful administrative assistance. I would also like to thank Lucia D'Amato for additional assistance during my PhD.

Finally, I want to thank my family: Daddy, Mummy, Linda chechi, and Denis chetta. Thank you for your patience and your unending love throughout my life.

\begin{flushright}
Lento Manickathan\\
\myMonthYear
\end{flushright}
