\refstepcounter{dummy}

%\pdfbookmark[0]{Curriculum Vitae}{cv}
\chapter{Curriculum Vitae}

\thispagestyle{empty}

\section*{Lento Manickathan}

\begin{tabular}{ll}
Date of birth	&  April 23, 1990\\ 
Place of birth	&  Schaffhausen, Switzerland\\ 
Nationality	& Indian \\ 
E-mail address	& lento.manickathan@gmail.com \\ 
\end{tabular} 

\vfill

\section*{Education}
\begin{tabular}{l p{10cm}}
2015 -- 2019  & Doctor of Sciences \\ 
~	&  ETH Zurich, Switzerland \\
2011 -- 2014  &  Master of Science in Aerospace Engineering\\ 
~	&  TU Delft, The Netherlands\\
2008 -- 2011  &  Bachelor of Science in Aerospace Engineering\\
~	&  TU Delft, The Netherlands \\
\end{tabular} 

\section*{Academic and Professional Experience}
\begin{tabular}{l p{10cm}}
	2015 -- 2019  & Scientific Assistant at ETH Zurich \\ 
	~	&  Zurich, Switzerland \\
	2012 &  Research Intern at Shell Global Solutions \\ 
	~	&  Rijswijk, The Netherlands\\
	2006 & Intern at Sulzer A.G. \\
	~ 	& Uster, Switzerland
\end{tabular} 

\vfill

\section*{Publications}
 
\subsection*{Journal}

\begin{enumerate}	
	\item \textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome, D., \& Carmeliet, J. (2018). Comparative study of flow field and drag coefficient of model and small natural trees in a wind tunnel. \textit{Urban Forestry \& Urban Greening}, 230–239. \url{http://doi.org/10.1016/j.ufug.2018.09.011}.
	
	\item \textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome, D., \& Carmeliet, J. (2018). Parametric study of the influence of environmental factors and tree properties on the transpirative cooling effect of trees. \textit{Agricultural and Forest Meteorology}, 248, 259–274. \url{http://doi.org/10.1016/j.agrformet.2017.10.014}.
\end{enumerate}

\subsection*{Conference}

\begin{enumerate}
	\item \textbf{Manickathan, L.}, Kubilay, A., Defraeye, T., Allegrini, J., Derome, D., Carmeliet, J.: Integrated vegetation model for studying the cooling potential of trees in urban street canyons. \textit{7th International Building Physics Conference}, Syracuse, NY, USA, September 23 - 26, 2018.
	
	\item \textbf{Manickathan, L.}, Kubilay, A., Defraeye, T., Allegrini, J., Derome, D., Carmeliet, J.: Integrated CFD vegetation model with soil-plant-air water dynamics for studying the cooling potential of vegetation in an urban street canyon. \textit{10th International Conference on Urban Climate/14th Symposium on the Urban Environment}, New York, NY, USA, 6 - 10 August 2018.
	
	\item \textbf{Manickathan, L.}, Kubilay, A., Defraeye, T., Allegrini, J., Derome, D., Carmeliet, J.: Conjugate soil-vegetation-air-radiation model for studying the environmental impact of porous media such as vegetation. \textit{Interpore 2018}, New Orleans, LA, USA, May 14 - 17, 2018.
	
	\item \textbf{Manickathan, L.}, Kubilay, A., Defraeye, T., Allegrini, J., Derome D., Carmeliet, J.: Influence of vegetation on pedestrian thermal comfort in a street canyon. \textit{1st International Conference on New Horizons in Green Civil Engineering}, Victoria, BC, Canada, April 25 - 27, 2018.
	
	\item \textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome, D., Carmeliet, J.: Transpirative cooling potential of vegetation in an urban environment using coupled CFD and leaf energy balance model. \textit{15th Conference of the International Building Performance Simulation Association}, San Francisco, CA, USA, 2017.
	
	\item \textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome, D., Carmeliet, J.: Conjugate Vegetation Model for Evaluating Evapotranspirative Cooling in Urban Environment. \textit{97th AMS Annual Meeting}, Seattle, WA, USA, 2017.
	
	\item \textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome, D., Carmeliet, J.: Aerodynamic characterization of model vegetation by wind tunnel experiments. \textit{4th International Conference on Countermeasures to Urban Heat Island}, Singapore, 2016.
\end{enumerate}

\subsection*{Preprint}

\begin{enumerate}
	\item \textbf{Manickathan, L.}, Defraeye, T., Carl, S., Richter, H., Allegrini, J., Derome, D., \& Carmeliet, J. (2019). Unveiling dynamic changes in the diurnal microclimate of a Buxus sempervirens with non-intrusive imaging of flow field, leaf temperature, and plant microstructure. \textit{Submitted to Agricultural and Forest Meteorology}. \url{https://arxiv.org/abs/1903.02283}.
	
	\item Palha, A., \textbf{Manickathan, L.}, Ferreira, C.S., van Bussel, G. (2016): A hybrid Eulerian-Lagrangian flow solver. \url{https://arxiv.org/abs/1505.03368v2}.
\end{enumerate}

\vfill

