%\begingroup
%\let\clearpage\relax
%\let\cleardoublepage\relax
%\let\cleardoublepage\relax
%\pdfbookmark[1]{Publications}{Publications}
%\addcontentsline{toc}{chapter}{Publications}
\refstepcounter{dummy}
\chapter{Publications}
\refstepcounter{dummy}

\section*{Journal}

The following publications are included in parts or in an extended version in this thesis:

\begin{enumerate}

	
	\item \textbf{Manickathan, L.}, Defraeye, T., Carl, S., Richter, H., Allegrini, J., Derome, D., \& Carmeliet, J. (2019). Unveiling dynamic changes in the diurnal microclimate of a Buxus sempervirens with non-intrusive imaging of flow field, leaf temperature, and plant microstructure. \textit{Submitted to Agricultural and Forest Meteorology}. (preprint: \url{https://arxiv.org/abs/1903.02283}).
	
	\item \textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome, D., \& Carmeliet, J. (2018). Comparative study of flow field and drag coefficient of model and small natural trees in a wind tunnel. \textit{Urban Forestry \& Urban Greening}, 230–239. \url{http://doi.org/10.1016/j.ufug.2018.09.011}.
	
	\item \textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome, D., \& Carmeliet, J. (2018). Parametric study of the influence of environmental factors and tree properties on the transpirative cooling effect of trees. \textit{Agricultural and Forest Meteorology}, 248, 259–274. \url{http://doi.org/10.1016/j.agrformet.2017.10.014}.


\end{enumerate}

\bigskip

\section*{Conference}

\begin{enumerate}
	\item \textbf{Manickathan, L.}, Kubilay, A., Defraeye, T., Allegrini, J., Derome, D., Carmeliet, J.: Integrated vegetation model for studying the cooling potential of trees in urban street canyons. \textit{7th International Building Physics Conference}, Syracuse, NY, USA, September 23 - 26, 2018.
	
	\item \textbf{Manickathan, L.}, Kubilay, A., Defraeye, T., Allegrini, J., Derome, D., Carmeliet, J.: Integrated CFD vegetation model with soil-plant-air water dynamics for studying the cooling potential of vegetation in an urban street canyon. \textit{10th International Conference on Urban Climate/14th Symposium on the Urban Environment}, New York, NY, USA, 6 - 10 August 2018.
	
	\item \textbf{Manickathan, L.}, Kubilay, A., Defraeye, T., Allegrini, J., Derome, D., Carmeliet, J.: Conjugate soil-vegetation-air-radiation model for studying the environmental impact of porous media such as vegetation. \textit{Interpore 2018}, New Orleans, LA, USA, May 14 - 17, 2018.
	
	\item \textbf{Manickathan, L.}, Kubilay, A., Defraeye, T., Allegrini, J., Derome D., Carmeliet, J.: Influence of vegetation on pedestrian thermal comfort in a street canyon. \textit{1st International Conference on New Horizons in Green Civil Engineering}, Victoria, BC, Canada, April 25 - 27, 2018.
	
	\item \textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome, D., Carmeliet, J.: Transpirative cooling potential of vegetation in an urban environment using coupled CFD and leaf energy balance model. \textit{15th Conference of the International Building Performance Simulation Association}, San Francisco, CA, USA, 2017.
	
	\item \textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome, D., Carmeliet, J.: Conjugate Vegetation Model for Evaluating Evapotranspirative Cooling in Urban Environment. \textit{97th AMS Annual Meeting}, Seattle, WA, USA, 2017.
	
	\item \textbf{Manickathan, L.}, Defraeye, T., Allegrini, J., Derome, D., Carmeliet, J.: Aerodynamic characterization of model vegetation by wind tunnel experiments. \textit{4th International Conference on Countermeasures to Urban Heat Island}, Singapore, 2016.
	
\end{enumerate}